Astrophysical calibration of gravitational-wave detectors

### 2015-10-07 docs/cosmic_cal.tex
Added short section on LISA verification binaries

\newcommand{\dcc}{LIGO-PXXXXXXXX}
\newcommand{\cm}[1]{\textcolor{red}{CM: #1}}
\newcommand{\MP}[1]{\textcolor{blue}{MP: #1}}
\newcommand{\lw}[1]{\textcolor{green}{LW: #1}}

@@

@@

% observing a coincident event
The most likely scenario in which a coincident \ac{GW}--\ac{sGRB} event would be identified is 
through the targeted follow-up of an observed \ac{GW} or by post-facto matching of \ac{GW} 
trigger lists with known \ac{sGRB} events.  The likelihood of being able to follow-up \ac{GW} 
events using gamma-ray telescopes with low enough latency to catch a \ac{sGRB} is low.  Compounding 
this issue is the relatively large \ac{GW} sky error-box giving a field-of-view for the \ac{EM} 
observatories to search spanning $\sim 100$'s of square degrees (e.g.\ 
\cite{2011CQGra..28j5021F,2013arXiv1304.0670L,2014ApJ...795..105S}).  For the \ac{GW} 
follow-up of \ac{sGRB} scenario the merger time for \ac{BNS}/\ac{NSBH} systems will be estimated 
from the \ac{sGRB} to within a few seconds (see e.g. the discussion in Sec.\ 2.2 of 
\cite{2012ApJ...760...12A}). This makes the follow-up search less 
computationally expensive since it is performed over a smaller range of data using potentially 
fewer numbers of waveform templates.  This computational saving enables the use of a more 
computationally expensive multi-detector coherent scheme rather than the cheaper coincidence 
methods used in the untargeted searches.

@@

We would like to acknowledge the useful discussions with a whole bunch of people. LW was part 
funded for this work through a Royal Astronomical Society Undergraduate Research Bursary.
MP is funded by the STFC under grant number ST/L000946/1 and CM is funded via
XXX.

>>>>

\newcommand{\dcc}{LIGO-P1500198}
\newcommand{\cm}[1]{\textcolor{red}{CM: #1}}
\newcommand{\MP}[1]{\textcolor{blue}{MP: #1}}
\newcommand{\lw}[1]{\textcolor{green}{LW: #1}}

@@

For future planned space-based detectors such as eLISA there are several known galactic binary 
systems known as ``verification'' binaries \cite{2006CQGra..23S.809S}, in that their masses and 
orbital parameters allow them to be guarenteed sources for such detectors. These too could be used 
for assessing calibiration for such detectors. However, generally for these verification binaries 
the inclination of the system is not known and distances are fairly uncertain, so an accurate 
calibration assessment may not be possible. Although there is at least one (J0651) currently known 
eclipsing white dwarf binary \cite{2041-8205-737-1-L23}, which does provide the system inclination 
\cite{2012ApJ...757L..21H, 2013ASPC..467...47K} and has an approximately 10\% distance uncertainty 
\cite{2041-8205-737-1-L23}, which make it an excellent candiate for an astrophysical calibrator at 
its frequency.

@@

% observing a coincident event
The most likely scenario in which a coincident \ac{GW}--\ac{sGRB} event would be identified is 
through the targeted follow-up of an observed \ac{GW} or by post-facto matching of \ac{GW} 
trigger lists with known (or subsequently found \cite{2015ApJS..217....8B}) \ac{sGRB} events.  
The likelihood of being able to follow-up \ac{GW} 
events using gamma-ray telescopes with low enough latency to catch a \ac{sGRB} is low.  Compounding 
this issue is the relatively large \ac{GW} sky error-box giving a field-of-view for the \ac{EM} 
observatories to search spanning $\sim 100$'s of square degrees (e.g.\ 
\cite{2011CQGra..28j5021F,2013arXiv1304.0670L,2014ApJ...795..105S}).  For the \ac{GW} 
follow-up of \ac{sGRB} scenario the merger time for \ac{BNS}/\ac{NSBH} systems will be estimated 
from the \ac{sGRB} to within a few seconds (see e.g. the discussion in Sec.\ 2.2 of 
\cite{2012ApJ...760...12A}). This makes the follow-up search less 
computationally expensive since it is performed over a smaller range of data using potentially 
fewer numbers of waveform templates.  This computational saving enables the use of a more 
computationally expensive multi-detector coherent scheme rather than the cheaper coincidence 
methods used in the untargeted searches.

@@

We would like to acknowledge the useful discussions with a whole bunch of people. LW was part 
funded for this work through a Royal Astronomical Society Undergraduate Research Bursary.
MP is funded by the STFC under grant number ST/L000946/1 and CM is funded via
XXX. This document has LIGO DCC number \dcc.
